---
title: "Automation Reliability in ATC: Mixed Model Analyses"
author: "ljgs"
date: "20/09/2021"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
by Luke Strickland

```{r load_packages_and_data, echo= FALSE , results = "hide", message=FALSE, warning=FALSE}


library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(car)
# library(lsmeans)
library(pander)
options(digits=2)
source("R/0-analysis_functions.R")

load("img/cleandats.RData")

cleandats <- cleandats %>% mutate(C = toupper(S)==R)

colnames(cleandats)[colnames(cleandats)=="sess"] <- "Session"
colnames(cleandats)[colnames(cleandats)=="cond"] <- "Condition"
colnames(cleandats)[colnames(cleandats)=="S"] <- "Stimulus"
colnames(cleandats)[colnames(cleandats)=="failtrial"] <- "Automation"

cleandats$Session <- factor(cleandats$Session, levels=c("1", "2", "3"),
                      labels=c("One", "Two", "Three"))

cleandats$Condition <- factor(cleandats$Condition , levels=c("AUTO_L", "AUTO_H", "MANUAL"),
                      labels=c("Automation_Low", "Automation_High", "Manual"))

cleandats$Automation <- factor(cleandats$Automation, levels=c("nonf", "fail"),
                      labels=c("Automation Success", "Automation Failure"))

cleandats$Stimulus <- factor(cleandats$Stimulus, levels=c("c", "n"),
                      labels=c("Conflict", "Non-conflict"))


tmp <- 1:24
tmp <- tmp[!tmp==4]
full_balance <- c(tmp, 28) 

cleandats <- cleandats %>% filter(s %in% full_balance)

theme_set(theme_simple())

accs <-
  cleandats %>% group_by(s, Stimulus, Condition, Automation, Session) %>% 
  filter(!is.na(R)) %>% summarise(acc = mean(C)) %>%
  arrange(s) %>% arrange(Automation)

RTs <- cleandats %>% group_by(s, Stimulus, Condition, Automation, Session) %>% 
  filter(C) %>% 
  summarise(RT=mean(RT))%>% arrange(Automation)


```


```{r check_participants,  echo= FALSE , results = "hide", message=FALSE, warning=FALSE}
accs_check <-
  cleandats %>% group_by(s, Condition, Automation, Session) %>% 
  filter(!is.na(R)) %>% summarise(acc = mean(C)) %>%
  arrange(s) %>% arrange(Automation)

accs_check %>% filter(acc<0.1)

accs_check %>% filter(acc<0.6 & Automation=="Automation Success")


```

```{r accuracy_descriptives_fortext, echo= FALSE, message=FALSE, warning=FALSE}
#Descriptives for text chunks
S <- accs %>% group_by(Stimulus) %>% summarise(mean(acc))
S_se <- se2(accs, facs="Stimulus", dvnam="acc")

sess <- accs %>% group_by(Session) %>% summarise(mean(acc))
sess_se <- se2(accs, facs="Session", dvnam="acc")

cond_auto <- accs %>% group_by(Condition, Automation) %>% summarise(mean(acc))
cond_auto_se <- arr2df(
  se2(accs, facs=c("Condition", "Automation"), dvnam="acc"))

# pandoc.table(cond_auto)
```

##### Accuracy
Participant accuracies are displayed in Figure 5. There were main effects of stimulus type, session, condition, and automation accuracy. Responses were more accurate to conflict trials 
(*M* = `r S[S$Stimulus=="Conflict",2]`, *SE* = `r S_se["Conflict"]`)
than to non-conflict trials
(*M* = `r S[S$Stimulus=="Non-conflict",2]`, *SE* = `r S_se["Non-conflict"]`).
Accuracy was lower on session one
(*M* = `r sess[sess$Session=="One",2]`, *SE* = `r sess_se["One"]`)
than on session two
(*M* = `r sess[sess$Session=="Two",2]`, *SE* = `r sess_se["Two"]`)
. The effects of automation condition and automation accuracy interacted. Participant accuracy was higher for trials where participants were provided correct automation (*M* = `r cond_auto[cond_auto$Condition=="Automation_High" & cond_auto$Automation=="Automation Success",3]`, 
*SE* = `r cond_auto_se[cond_auto_se$Condition=="Automation_High" & cond_auto_se$Automation=="Automation Success",3]`) than for corresponding manual trials (*M* = `r cond_auto[cond_auto$Condition=="Manual" & cond_auto$Automation=="Automation Success",3]`, 
*SE* = `r cond_auto_se[cond_auto_se$Condition=="Manual" & cond_auto_se$Automation=="Automation Failure",3]`), and lower when participants were provided incorrect automation (*M* = `r cond_auto[cond_auto$Condition=="Automation_High" & cond_auto$Automation=="Automation Failure",3]`, 
*SE* = `r cond_auto_se[cond_auto_se$Condition=="Manual" & cond_auto_se$Automation=="Automation Failure",3]`), as compared with matched manual trials (*M* = `r cond_auto[cond_auto$Condition=="Manual" & cond_auto$Automation=="Automation Failure",3]`, 
*SE* = `r cond_auto_se[cond_auto_se$Condition=="Manual" & cond_auto_se$Automation=="Automation Failure",3]`). These results suggest that participants did use the automation to their advantage, but on trials where the automation failed, it imposed a substantial cost to their accuracy. However, importantly, accuracy on automation incorrect trials was far from floor, suggesting that participants did not rely on the automation entirely.


```{r echo= FALSE}
acc_cap <- "*Figure 5.* Conflict detection accuracies. Each panel corresponds to one stimulus type, on one experimental session. The error bars included were calculated using the Morey (2008) bias-corrected method for within-subjects error bars."
```


```{r response_accuracy_graph, echo= FALSE, message=FALSE, warning=FALSE,fig.height = 8, fig.width = 13,fig.cap=acc_cap}
mean_accs <- accs %>% group_by(Stimulus, Condition, Automation) %>%
  summarise(meanacc=mean(acc))

searr= se2(accs, facs= c("Stimulus", "Condition", "Automation"),
dvnam="acc", sfac="s")
se_accs <- as.data.frame.table(searr)
colnames(se_accs)[colnames(se_accs)=="Freq"] <- "seacc"

plot.df <- full_join(mean_accs, se_accs)

plot.df$Automation <- factor(plot.df$Automation, 
                             levels=c("Automation Success", "Automation Failure"),
                             labels= c("Automation Correct", "Automation Incorrect"))

ggplot(plot.df, aes(Automation, meanacc)) +geom_point(aes(col=Condition, shape=Condition), size=3)  + 
  facet_grid(.~Stimulus) + geom_errorbar(aes(
    ymax = meanacc + seacc,
    ymin = meanacc - seacc,
    colour = Condition, width = 0.3
  )) +ylab ("Accuracy") +xlab("") +
    theme(text = element_text(size = 21))

```


```{r RT_descriptives_fortext, echo= FALSE, message=FALSE, warning=FALSE}
#Descriptives for text chunks
S_RT <- RTs %>% group_by(Stimulus) %>% summarise(mean(RT))
S_se_RT <- se2(RTs, facs="Stimulus", dvnam="RT")

sess_cond_RT <- RTs %>% group_by(Session, Condition) %>% summarise(mean(RT))
sess_cond_se_RT <- se2(RTs, facs=c("Session", "Condition"), 
                    dvnam="RT")

cond_auto_RT <- RTs %>% group_by(Condition, Automation) %>% summarise(mean(RT))
cond_auto_se_RT <- arr2df(
  se2(RTs, facs=c("Condition", "Automation"), dvnam="RT"))

# pandoc.table(cond_auto_RT)


RTs_nos3 <- cleandats %>% filter(block!="three" & Session!="Three") %>% group_by(s, Stimulus, Condition, Automation, Session) %>% 
  filter(C) %>% 
  summarise(RT=mean(RT))%>% arrange(Automation)


cond_auto_RT_nos3 <- RTs_nos3 %>% group_by(Condition, Automation) %>% summarise(mean(RT))

# pandoc.table(cond_auto_RT_nos3)

```


##### Response Times
Mean correct RTs are displayed in Figure 6. There were main effects of stimulus type, session, condition, and automation accuracy. Correct responses were slower to conflict trials 
(*M* = `r S_RT[S_RT$Stimulus=="Conflict",2]`, *SE* = `r S_se_RT["Conflict"]`)
than to non-conflict trials
(*M* = `r S_RT[S_RT$Stimulus=="Non-conflict",2]`, *SE* = `r S_se_RT["Non-conflict"]`). The effects of condition and automation accuracy interacted. Correct RTs were not substantially slower on trials where participants were provided correct automation 
(*M* = `r cond_auto_RT %>% filter(Automation=='Automation Success' & Condition=="Automation_High") %>% 
pull('mean(RT)')` *SE* = `r cond_auto_se_RT %>% filter(Automation=='Automation Success' & Condition=="Automation_High") %>% 
.$y`)
than on corresponding manual trials (*M* = `r cond_auto_RT %>% filter(Automation=='Automation Success' & Condition=='Manual') %>% 
pull('mean(RT)')` *SE* = `r cond_auto_se_RT %>% filter(Automation=='Automation Success' & Condition=='Manual') %>% 
.$y`). By contrast, there were large differences in correct RT between automation-incorrect trials
(*M* = `r cond_auto_RT %>% filter(Automation=='Automation Failure' & Condition=="Automation_High") %>% 
pull('mean(RT)')` *SE* = `r cond_auto_se_RT %>% filter(Automation=='Automation Failure' & Condition=="Automation_High") %>% 
.$y`)
and matched manual trials (*M* = `r cond_auto_RT %>% filter(Automation=='Automation Failure' & Condition=='Manual') %>% 
pull('mean(RT)')` *SE* = `r cond_auto_se_RT %>% filter(Automation=='Automation Failure' & Condition=='Manual') %>% 
.$y`). The effects of condition and session also interacted. On session one,
RTs were slower in the automation condition
(*M* = `r sess_cond_RT %>% filter(Session=='One' & Condition=="Automation_High") %>% 
pull('mean(RT)')`,
*SE* = `r sess_cond_se_RT["One", "Automation_High"]`)
than in the manual condition
(*M* = `r sess_cond_RT %>% filter(Session=='One' & Condition=='Manual') %>% 
pull('mean(RT)')`,
*SE* = `r sess_cond_se_RT["One", "Manual"]`)
.
On session two, 
RTs were less substantially slower in the automation condition
(*M* = `r sess_cond_RT %>% filter(Session=='Two' & Condition=="Automation_High") %>% 
pull('mean(RT)')`,
*SE* = `r sess_cond_se_RT["Two", "Automation_High"]`)
than in the manual condition
(*M* = `r sess_cond_RT %>% filter(Session=='Two' & Condition=='Manual') %>% 
pull('mean(RT)')`,
*SE* = `r sess_cond_se_RT["Two", "Manual"]`), though the magnitude of the difference was greatly attenuated relative to session 1, with the difference failing to cross the p < .005 threshold. 


```{r echo= FALSE}
RT_cap <- "*Figure 6.* Correct conflict detection response times (RT). Each panel corresponds to responses to one type of stimulus on one experimental session. The error bars included were calculated using the Morey (2008) bias-corrected method for within-subjects error bars."
```


```{r response_RT_graph 1, echo= FALSE, message=FALSE, warning=FALSE,fig.height = 8, fig.width = 13,fig.cap=RT_cap}
mean_RTs <- RTs %>% group_by(Stimulus, Condition, Automation,Session) %>% summarise(meanRT=mean(RT))

searr= se2(RTs, facs= c("Stimulus", "Condition", "Automation", "Session"), dvnam="RT", sfac="s")
se_RTs <- as.data.frame.table(searr)
colnames(se_RTs)[colnames(se_RTs)=="Freq"] <- "seRT"



plot.df <- full_join(mean_RTs, se_RTs)

plot.df$Automation <- factor(plot.df$Automation, 
                             levels=c("Automation Success", "Automation Failure"),
                             labels= c("Automation Correct", "Automation Incorrect"))

ggplot(plot.df, aes(Automation, meanRT)) +geom_point(aes(col=Condition, shape=Condition), size=3)  + 
   ylab("Mean RT")+ xlab("") +
  facet_grid(Session~Stimulus) + geom_errorbar(aes(
    ymax = meanRT + seRT,
    ymin = meanRT - seRT,
    colour = Condition, width = 0.3
  ))  +
    theme(text = element_text(size = 21))
```
